Learning communication systems through recursive pragmatic reasoning about other agents

### 2013-05-31 praglearn.tex
models ection

\title{Learning to communicate using recursive pragmatic
  reasoning about other agents}
% \title{Learning words via recursive pragmatic reasoning about other agents}
% : The blessing of social anxiety - not a huge fan of colon titles

@@

\newcommand{\word}{\text{word}}
\newcommand{\obj}{\text{object}}
\newcommand{\lex}{\text{lexicon}}
\newcommand{\prior}{P_{\text{prior}}(\obj | \text{context})}

@@

\begin{abstract}
  Language users are remarkably good at making inferences about
  speakers' intentions in context, and children learning their native
  language also display substantial skill in acquiring the
  meanings of unknown words. These two cases are deeply related:
  Language users invent new terms in conversation, and language
  learners learn the literal meanings of words based on their
  pragmatic inferences about how those words are used. 
 While pragmatic inference and word
  learning have both been independently characterized in probabilistic
  terms, no current work unifies these two. We describe a
  model in which language learners assume that they jointly
  approximate a shared, external lexicon and reason recursively about
  the goals of others in using this lexicon. This model captures
  phenomena in word learning and pragmatic inference; it additionally
  leads to insights about the emergence of communicative systems in
  conversation and the mechanisms by which pragmatic inferences become
  incorporated into word meanings.
\end{abstract}

@@

Natural language is a powerful tool for conveying meaning in
context. Consider
``it's raining,'' ``I ate some of the cookies,'' or ``can you close
the window?'' In each, a listener must go beyond the literal meaning
of the words to fill in contextual details (``it's raining here and
now''), infer that a stronger alternative is not true (``I ate some
but not all of the cookies''), or more generally infer the speaker's
communicative goal (``I want you to close the window right now because
I'm cold''), a process known as \textit{pragmatic reasoning}. 
This kind of pragmatic reasoning is core to language use,

@@

\subsection{Paradoxes in optimal models of pragmatic learning}
% When modelling human behavior, it's useful to begin with optimal
% models; this has the advantage that when we are then forced to
% deviate from the purely rational approach, it's generally in a
% theoretically interpretable way. However,
Multi-agent interactions are difficult to model in a normative or
optimal framework without falling prey to paradox. For example,
consider a simple model of the agents in the above game. First we
define a \textit{literal listener} $L_0$. This agent has a
\textit{lexicon} which probabilistically maps words to meanings;
specifically, it assigns each word $w$ a vector describing the extent
to which this word provides evidence for each possible object.\footnote{We
  assume words refer directly to objects, rather than to abstract
  semantic features. Our simplification is without loss of
  generalization, however, because we can interpret our model as
  marginalizing over such a representation, with our literal
  $P_\lex(\obj | \word) = \sum_\text{features} P(\obj |
  \text{features}) P_\lex(\text{features} | \word)$.} Each entry in
the vector is in $(0, 1)$, and together they sum to 1:
\begin{align*}
P_{L_0}(\obj | \word, \lex) &\propto \lex(\word, \obj) \times \prior.
\end{align*}
Confronted with such a listener, a probabilistically rational speaker
should attempt to choose a word which soft-maximizes the probability
that the listener will assign to the target object---modulated by the
effort or cost associated with producing this word:
\begin{align*}
P_{S_1}(\word | \obj, \lex) &\propto \exp\Big(\lambda \big(\log P_{L_0}(\obj | \word, \lex) - \text{cost}(\word)\big)\Big).
\end{align*}
But given this speaker, then the naive $L_0$ strategy is not
optimal. Instead, listeners should use Bayes rule to invert the
speaker's decision procedure \cite{frank2012}:
\begin{align*}
P_{L_2}(\obj | \word, \lex) &\propto P_{S_1}(\word | \obj, \lex) \times \prior.
\end{align*}
Now the paradox becomes apparent. Given such a listener, it is no
longer optimal for speakers to implement strategy $S_1$; instead, they
should implement strategy $S_3$ which soft-maximizes $P_{L_2}$ instead
of $P_{L_0}$. And then listeners ought to implement $L_4$, and so on.

One computationally expensive option is to continue iterating such
strategies until reaching a fixed point equilibrium. While this
strategy guarantees that each agent will behave normatively given the
other agent's strategy, there is no guarantee that such strategies
will be near the system's global optimum; equilibrium strategies make
up only a small subspace of all possible strategies. Nor is there much
evidence the humans find such equilibria; their behavior in language
games (and in other games \cite{camerer2004}) can be well-modeled as
implementing $S_n$ or $L_n$ for some small $n$
\cite{frank2012}. Following this work, we recurse a finite (small)
number of times. The consequence is that one agent, implementing
$S_n$, is fully optimal with respect to the game, while the other,
implementing $L_{n-1}$, is nearly optimal---off by only a single
recursion.

@@

To add insult to injury, one final problem is that there is nothing
constraining speaker and listener to use the same language under this
model. In principle, so long as the listener has a good model of the
speaker, and the speaker has a good model of the listener, then
communication succeeds. This result clearly presents a dramatic
mismatch to typical human communication, which almost never proceeds
with distinct languages spoken by each participant.

@@

Assumption (a) corresponds to the lexicographer's illusion: Naive
language users will argue vociferously that words have specific
meanings, even though these meanings are unobservable to everyone who
purportedly uses them. It also explains why learners speak the
language they hear (rather than some private language that they assume
listeners will eventually learn): Under assumption (a), observing
other speakers' behavior provides data about not just that speaker's
idiosyncratic lexicon, but the consensus lexicon. Assumption (b)
avoids the explosion of hyper$^n$-distributions described above: If
agent $n$ knows the lexicon, they assume that all lower agents do as
well, reducing to the original tractable model without
uncertainty. And assumption (c) introduces a limited form of
uncertainty, and thus the potential for learning.
% Everything else follows by applying standard Bayesian reasoning
% given these assumptions.

Formally, let an unadorned $L$ and $S$ denote our socially-anxious
listener and speaker. $L$ inverts their marginal distribution over the
speaker; $S$ soft-maximizes their marginal distribution over the
listener. With $L_i$ and $S_i$ as above, this gives:
\begin{align*}
  P_L(\obj | \word) &= P_{S_{n-1}}(\word | \obj, \text{$L$'s data}) \times \prior \\
    &= \sum_\lex P_{S_{n-1}}(\word | \obj, \lex) \times P(\lex | \text{$L$'s data}) \times \prior \\
    &= P_{L_n}(\obj | \word, \text{$L$'s data}). \\
  P_S(\word | \obj) &\propto \exp\Big(\lambda \big(\log P_{L_n}(\obj | \word, \text{$S$'s data}) - \text{cost}(\word)\big)\Big).
\end{align*}
Here $L$'s data consists of $S$'s utterances together with whatever
other information $L$ may have about their meaning (e.g.~from
contextual clues). By assumption (b), $L$ treats these as utterances
as samples from the knowledgeable speaker $S_{n-1}$, not $S$, and thus
as being informative about the lexicon. Similarly, $S$ may observe
$L$'s interpretations of various utterances, and will treat these as
samples from $L_n$, not $L$.

In several important cases, these assumptions are as close to rational
as possible within the finite-recursion framework. If $L_n(\obj |
\word, \text{$S$'s data})$ and $L_n(\obj | \word, \text{$L$'s data})$
coincide, then $S$ is fully normative and $L$ is off by only a single
recursion. This case in particular includes all previous experiments
using this pragmatic reasoning framework, which considered only
single-turn interactions where $\text{$L$'s data} = \text{$S$'s data}
= \emptyset$. Alternatively, if one agent has enough data that their
uncertainty is effectively non-existent, then it becomes normative for
their partner to treat them as being fully knowledgeable, and this is
a reasonable description of the child language learning case. In
general, though, in arbitrary multi-turn interactions in which both
agents have non-trivial uncertainty, this model induces complex and
non-normative learning dynamics.

@@

\begin{table}[t]
\label{tab:results}
\begin{center}
\begin{tabular}{lccccc}
\toprule
Phenomenon & Ref. & WL & PI & PI+U & PIL \\
\midrule
Interpreting specificity implicature & \cite{grice1975} &  & x &x & x\\
Interpreting Horn implicature & \cite{horn1984} & &  & x& x\\
Cross-situational learning & \cite{smith2008} & x& & & x \\
Disambiguating new words using old words & \cite{markman1988} &x  & & & x \\
Disambiguation without mapping & \cite{horst2008} &  & & & x \\
Emergence of novel \& efficient communicative systems & \cite{galantucci2005} & & & & x \\
Lexicalization of Horn implicature & \cite{horn1984} & & & & x \\
Non-lexicalization of specificity implicature & \cite{levinson2000} & & & & x \\
\hline
\end{tabular}
\end{center}
\caption{Empirical results and references. WL refers to the word
  learning model of \cite{frank2009}; PI refers to the recursive
  pragmatic inference model of \cite{frank2012}; PI+U refers to the
  pragmatic inference model of \cite{bergen2012} which includes
  lexical uncertainty, marginalizes it out, and then recurses. Our
  current model is referred to here as PIL, or pragmatic inference and
  learning.}
\end{table}

@@

\label{sec:spec}

@@

The recursive pragmatic reasoning portions of our model capture
findings on specificity implicature. Consider a representation of
scalar implicature as a matrix $\left[
    \begin{array}{cc}
      0.5 & 0.5 \\
      0 & 1
    \end{array}
  \right]$, where rows show the words ``some'' and ``all'' and columns
  indicate worlds where {\sc some but not all} and {\sc all} are true,
  respectively, capturing the regularity that ``some'' can be said of
  situations where {\sc all} is actually the case. Assuming uniform
  costs for the two words, a rational speaker confronted with such a
  lexicon will prefer to say ``some'' only when they mean \textsc{some
    but not all}, and this is therefore the interpretation that a
  rational listener will place on ``some'' as well. To simulate this
  situation, we place a Dirichlet(10, 10) prior on the meaning of
  \textit{some} and a Dirichlet(1, 10) prior on the meaning of
  \textit{all}, giving speaker probabilities of
  $\left[
    \begin{array}{cc}
      1.00 & 0.00 \\
      0.00 & 1.00
    \end{array}
  \right]$
and listener probabilities of
$\left[
    \begin{array}{cc}
      .86 & .14 \\
      .03 & .97
    \end{array}
  \right]$. These revised interpretation probabilities minimize
  ambiguity (with weight concentrated on the diagonal), capturing the specificity implicature.

@@

\subsection{Preservation of specificity implicatures}
\label{sec:learning-specificity-implic}

@@

The acquisition of scalar adjectives like ``some'' provides a puzzle
for most models of word learning: given that in many contexts, the
word ``some'' is used to mean \textsc{some-but-not-all}, how do
children learn that {\sc some-but-not-all} is not in fact its literal meaning? Our model
is able to take specificity implicatures into account when learning,
and thus provide a potential solution, congruent with the observation
that no known language in fact lexicalizes {\sc some-but-not-all}.

Following the details of \S\ref{sec:spec}, we created a simulation in
which the meaning of ``all'' was fixed to be a particular set {\sc
  all}, and where the learner must infer the meaning of ``some,''
distinguishing two possible meanings: {\sc some-but-not-all}
(unambiguous, 
pragmatically strengthened) or
{\sc some-but-not-all or all} (ambiguous). Training exposure in the
simulation consisted of situations in which ``some'' was pragmatically
strengthened to refer to {\sc some-but-not-all}. Despite this
unambiguous training, the model maintained substantial
posterior probability on the correct (ambiguous) hypothesis about the
meaning of ``some.'' In each
situation, the model essentially reasoned that although the evidence
was unambiguous, it could have been produced by an implicature and
hence should be discounted. Thus, a pragmatically-informed learner
might both be able to maintain the true meaning of {\sc some} and
interpret it correctly as denoting {\sc some-but-not-all} in
appropriate contexts.

% Exposure to these
% situations does not result in mapping of ``some'' to {\sc
%   some-but-not-all}, despite the evidence that 
% Imagine two bowls: one
% containing a mixture of apples and oranges, the other containing
% apples alone. After encountering the words ``some'' and ``all'' used contrastively
% to refer to these two bowls (as in e.g.\ ``the bowl with some
% apples''), a learner under our model believes that at least one of these words must have a
% restrictive literal meaning, but not both---it leaves open the
% possibility that either ``some'' or ``all'' might be literally
% ambiguous. But if examples of ``some'' are given that refer to exactly
% the same object in contexts where this is the only object
% available, so there is no contrast and thus no implicature; this
% convinces the model that ``all apple'' literally refers only to the
% bowl that contains no oranges, while ``some'' most likely is somewhat
% ambiguous. Crucially, the model is able to learn this without once
% ever observing ``some'' used

% s1: reasonable chance that ``some'' literally refers to only one, but
% maybe ``some'' refers to both. so you can learn ambiguity even with
% unambiguous evidence.

% s2:

>>>>

\title{Learning communication systems through recursive pragmatic
  reasoning about other agents}
% \title{Learning words via recursive pragmatic reasoning about other agents}
% : The blessing of social anxiety - not a huge fan of colon titles

@@

\newcommand{\word}{\text{word}}
\newcommand{\obj}{\text{object}}
\newcommand{\lex}{\text{lexicon}}
%\newcommand{\prior}{P_{\text{prior}}(\obj | \text{context})}
\newcommand{\prior}{P_{\text{prior}}(\obj)}

@@

\begin{abstract}
  Language users are remarkably good at making inferences about
  speakers' intentions in context, and children learning their native
  language also display substantial pragmatic skill in acquiring the
  meanings of unknown words. While pragmatic inference and word
  learning have both been characterized in probabilistic terms, no
  current models make appropriate inferences about the meanings of
  words in pragmatically-rich inferential contexts. We describe a
  model in which language learners assume that they jointly
  approximate a shared, external lexicon and reason recursively about
  the goals of others in using this lexicon. This model captures
  phenomena in word learning and pragmatic inference; it additionally
  leads to insights about the emergence of communicative systems in
  conversation and the mechanisms by which pragmatic inferences become
  incorporated into word meanings.
\end{abstract}

@@

Natural language is a powerful tool for conveying meaning in
context. Our utterances are pervasively underspecified. Consider
``it's raining,'' ``I ate some of the cookies,'' or ``can you close
the window?'' In each, a listener must go beyond the literal meaning
of the words to fill in contextual details (``it's raining here and
now''), infer that a stronger alternative is not true (``I ate some
but not all of the cookies''), or more generally infer the speaker's
communicative goal (``I want you to close the window right now because
I'm cold''), a process known as \textit{pragmatic reasoning}.

@@

\subsection{Paradoxes in optimal models of pragmatic learning}
% When modelling human behavior, it's useful to begin with optimal
% models; this has the advantage that when we are then forced to
% deviate from the purely rational approach, it's generally in a
% theoretically interpretable way. However,
Multi-agent interactions are difficult to model in a normative or
optimal framework without falling prey to paradox. For example,
consider a simple model of the agents in the above game. First we
define a \textit{literal listener} $L_0$. This agent has a
\textit{lexicon} of associations between words and meanings;
specifically, it assigns each word $w$ a vector of numbers in $(0, 1)$ describing the extent
to which this word provides evidence for each possible object\footnote{We
  assume words refer directly to objects, rather than to abstract
  semantic features. Our simplification is without loss of
  generalization, however, because we can interpret our model as
  marginalizing over such a representation, with our literal
  $P_\lex(\obj | \word) = \sum_\text{features} P(\obj |
  \text{features}) P_\lex(\text{features} | \word)$.}.%
If we assume the listener simply re-weights their prior expectation   
about what is referred to using their lexicon:
\begin{align*}
P_{L_0}(\obj | \word, \lex) &\propto \lex(\word, \obj) \times \prior.
\end{align*}
Because of the normalization in this equation, there is a systematic but unimportant symmetry among lexicons; we 
remove this by assuming the lexicon sums to $1$ over objects for each word.
Confronted with such a listener, a probabilistically rational speaker
should attempt to choose a word which soft-maximizes the probability
that the listener will assign to the target object---modulated by the
effort or cost associated with producing this word:
\begin{align*}
P_{S_1}(\word | \obj, \lex) &\propto \exp\Big(\lambda \big(\log P_{L_0}(\obj | \word, \lex) - \text{cost}(\word)\big)\Big).
\end{align*}
But given this speaker, then the naive $L_0$ strategy is not
optimal. Instead, listeners should use Bayes rule to invert the
speaker's decision procedure \cite{frank2012}:
\begin{align*}
P_{L_2}(\obj | \word, \lex) &\propto P_{S_1}(\word | \obj, \lex) \times \prior.
\end{align*}
Now the paradox becomes apparent. Given such a listener, it is no
longer optimal for speakers to implement strategy $S_1$; instead, they
should implement strategy $S_3$ which soft-maximizes $P_{L_2}$ instead
of $P_{L_0}$. And then listeners ought to implement $L_4$, and so on.

One option is to continue iterating such
strategies until reaching a fixed point equilibrium. While this
strategy guarantees that each agent will behave normatively given the
other agent's strategy, there is no guarantee that such strategies
will be near the system's global optimum. More importantly, is there much
evidence that humans do not use such equilibrium strategies; their behavior in language
games (and in other games \cite{camerer2004}) can be well-modeled as
implementing $S_n$ or $L_n$ for some small $n$
\cite{frank2012}. Following this work, we recurse a finite (small)
number of times. The consequence is that one agent, implementing
$S_n$, is fully optimal with respect to the game, while the other,
implementing $L_{n-1}$, is only nearly optimal---off by a single
recursion.

@@

One final problem is that there is nothing
constraining speaker and listener to use the same language under this
model. In principle, so long as the listener has a good model of the
speaker, and the speaker has a good model of the listener, then
communication succeeds. This result clearly presents a dramatic
mismatch to typical human communication, which almost never proceeds
with distinct languages spoken by each participant.

@@

Assumption (a) corresponds to the lexicographer's illusion: Naive
language users will argue vociferously that words have specific
meanings, even though these meanings are unobservable to everyone who
purportedly uses them. It also explains why learners speak the
language they hear (rather than some private language that they assume
listeners will eventually learn): Under assumption (a), observing
other speakers' behavior provides data about not just that speaker's
idiosyncratic lexicon, but the consensus lexicon. Assumption (b)
avoids the explosion of hyper$^n$-distributions described above: If
agent $n$ knows the lexicon, they assume that all lower agents do as
well, reducing to the original tractable model without
uncertainty. And assumption (c) introduces a limited form of
uncertainty at the top level, and thus the potential for learning.
% Everything else follows by applying standard Bayesian reasoning
% given these assumptions.

Formally, let an unadorned $L$ and $S$ denote our convention-based
listener and speaker. By assumption (c), the top-level listener has uncertainty over the lexicon; if the lexicon were known they would draw inferences as in $L_n$ above:
%\begin{align*}
%  P_L(\obj | \word) &= P_{S_{n-1}}(\word | \obj, \text{$L$'s data}) \times \prior \\
%    &= \sum_\lex P_{S_{n-1}}(\word | \obj, \lex) \times P(\lex | \text{$L$'s data}) \times \prior. \\
%    &= P_{L_n}(\obj | \word, \text{$L$'s data}). \\
%  P_S(\word | \obj) &\propto \exp\Big(\lambda \big(\log P_{L_n}(\obj | \word, \text{$S$'s data}) - \text{cost}(\word)\big)\Big).
%\end{align*}
%
\begin{align*}
  P_L(\obj | \word, \text{$L$'s data}) &=  \sum_\lex P_{L_n}(\obj | \word, \lex) P(\lex | \text{$L$'s data}) \\
\end{align*}
Here $L$'s data consists of $S$'s utterances together with whatever
other information $L$ may have about their meaning (e.g.~from
contextual clues). 
By assumption (b), $L$ treats these  utterances
as samples from the knowledgeable speaker $S_{n-1}$, not $S$, and thus
as being informative about the lexicon. For instance, when the data is a set of fully observed 
word-referent pairs $\{w_i, o_i\}$:
\begin{align*}
  P(\lex | \text{$L$'s data}) \propto P(\lex) \prod_i P_{S_{n-1}}(w_i|o_i,  \lex)
\end{align*}
The top-level speaker attempts to select the word which soft-maximizes their utility, with utility now being defined in terms of the informativity of the expectation (over lexicons) that the listener will have for at the right referent\footnote{An alternative model would have the speaker take the expectation over informativity, instead of the informativity of the expectation.}:
\begin{align*}
  P_S(\word | \obj, \text{$S$'s data}) &\propto \exp\Big(\lambda \big(\log  \sum_\lex P_{L_{n-1}}(\obj | \word, \lex) P(\lex|\text{$S$'s data}) - \text{cost}(\word)\big)\Big)
\end{align*}
Here $P(\lex|\text{$S$'s data}$ is defined similarly, when $S$ observes
$L$'s interpretations of various utterances, and treats them as
samples from $L_n$, not $L$.

%In several important cases, these assumptions are as close to rational
%as possible within the finite-recursion framework. If $L_n(\obj |
%\word, \text{$S$'s data})$ and $L_n(\obj | \word, \text{$L$'s data})$
%coincide, then $S$ is fully normative and $L$ is off by only a single
%recursion. This case in particular includes all previous experiments
%using this pragmatic reasoning framework, which considered only
%single-turn interactions where $\text{$L$'s data} = \text{$S$'s data}
%= \emptyset$.

If the speaker has enough data that their
uncertainty is effectively non-existent, then it becomes normative for
their partner to treat them as being fully knowledgeable, and this is
a reasonable description of the child language learning case. In
general, though, in arbitrary multi-turn interactions in which both
agents have non-trivial uncertainty, this model induces complex and
non-normative learning dynamics.

@@

\begin{table}[t]
\label{tab:results}
\begin{center}
\begin{tabular}{lccccc}
\toprule
Phenomenon & Ref. & WL & PI & PI+U & PIL \\
\midrule
Interpreting specificity implicature & \cite{grice1975} &  & x &x & x\\
Interpreting Horn implicature & \cite{horn1984} & &  & x& x\\
Cross-situational learning & \cite{smith2008} & x& & & x \\
Disambiguating new words using old words & \cite{markman1988} &x  & & & x \\
Disambiguation without mapping & \cite{horst2008} &  & & & x \\
Emergence of novel \& efficient communicative systems & \cite{galantucci2005} & & & & x \\
Lexicalization of Horn implicature & \cite{horn1984} & & & & x \\
Lexicalization of specificity implicature & \cite{levinson2000} & & & & x \\
\hline
\end{tabular}
\end{center}
\caption{Empirical results and references. WL refers to the word
  learning model of \cite{frank2009}; PI refers to the recursive
  pragmatic inference model of \cite{frank2012}; PI+U refers to the
  pragmatic inference model of \cite{bergen2012} which includes
  lexical uncertainty, marginalizes it out, and then recurses. Our
  current model is referred to here as PIL, or pragmatic inference and
  learning.}
\end{table}

@@

@@

The recursive pragmatic reasoning portions of our model capture
findings on specificity implicature. Consider a representation of
scalar implicature as a matrix $\left[
    \begin{array}{cc}
      0.5 & 0.5 \\
      0 & 1
    \end{array}
  \right]$, where rows show the words ``some'' and ``all'' and columns
  indicate worlds where {\sc some but not all} and {\sc all} are true,
  respectively, capturing the regularity that ``some'' can be said of
  situations where {\sc all} is actually the case. Assuming uniform
  costs for the two words, a rational speaker confronted with such a
  lexicon will prefer to say ``some'' only when they mean \textsc{some
    but not all}, and this is therefore the interpretation that a
  rational listener will place on ``some'' as well. To simulate this
  situation, we place a Dirichlet(10, 10) prior on the meaning of
  \textit{some} and a Dirichlet(1, 10) prior on the meaning of
  \textit{all}, and find this gives speaker use probabilities of
  $\left[
    \begin{array}{cc}
      1.00 & 0.00 \\
      0.00 & 1.00
    \end{array}
  \right]$
and listener interpretation probabilities of
$\left[
    \begin{array}{cc}
      .86 & .14 \\
      .03 & .97
    \end{array}
  \right]$.

@@

\subsection{Lexicalization and preservation of specificity implicature}
\label{sec:learning-specificity-implic}

@@

The acquisition of scalar adjectives like ``some'' provides a puzzle
for most models of word learning: given that in many contexts, the
word ``some'' is used to mean \textsc{some but not all}, how do
children learn that {\sc some but not all} is not in fact its literal meaning? Our model
is able to take specificity implicatures into account when learning,
and thus provide a potential solution.

Imagine two bowls: one
containing a mixture of apples and oranges, the other containing
apples alone. After encountering the words ``some'' and ``all'' used contrastively
to refer to these two bowls (as in e.g.\ ``the bowl with some
apples''), a learner under our model believes that at least one of these words must have a
restrictive literal meaning, but not both---it leaves open the
possibility that either ``some'' or ``all'' might be literally
ambiguous. But if examples of ``some'' are given that refer to exactly
the same object in contexts where this is the only object
available, so there is no contrast and thus no implicature; this
convinces the model that ``all apple'' literally refers only to the
bowl that contains no oranges, while ``some'' most likely is somewhat
ambiguous. Crucially, the model is able to learn this without once
ever observing ``some'' used
